### 2014-12-11 paper.tex
backpointer talk

\titleformat{\section}{\normalsize\bf}{\thesection \hspace{5pt}}{0em}{}
\titleformat{\subsection}{\normalsize\bf}{\thesubsection \hspace{5pt}}{0em}{}

@@

\centerline{\large{\textbf{Distributed Multi-Heuristic A* (HAMSTAR)}}}
\centerline{Noam Brown, Aram Ebtekar, Yuzuko Nakamura}
\centerline{15-712 Fall 2014 Final Project Report}

@@

\textbf{Interprocess communication with MPI}

@@

\textbf{Synchronous broadcast vs. asynchronous sync-ups}

@@

\textbf{Update collation performed at anchor node}

\textbf{Update collation performed at anchor node}

@@

\textbf{Back-pointer optimization}

$bp(s)$ is a pointer to the parent of $s$ along the optimal path found so far from the start to $s$. It is not needed to perform the search and compute a conservative distance to the goal; it is only used to reconstruct the path once the search terminates.

>>>>

%\titleformat{\section}{\normalsize\bf}{\thesection \hspace{5pt}}{0em}{}
%\titleformat{\subsection}{\normalsize\bf}{\thesubsection \hspace{5pt}}{0em}{}

@@

\centerline{\Large{\textbf{Distributed Multi-Heuristic A* (HAMSTAR)}}}
\centerline{Noam Brown, Aram Ebtekar, Yuzuko Nakamura}
\centerline{15-712 Fall 2014 Final Project Report}

@@

\subsubsection*{Interprocess communication with MPI}

@@

\subsubsection*{Synchronous broadcast vs. asynchronous sync-ups}

@@

\subsubsection*{Update collation performed at anchor node}

@@

\subsubsection*{Back-pointer optimization}

$bp(s)$ represents the parent of $s$ along the optimal path found so far from the start to $s$. As a single pointer cannot be shared across a distributed replicated data structure, our first implementation used a full state representation (5x5 sliding tile puzzle) in place of $bp(s)$, nearly doubling the length of network messages. However, notice that $bp(s)$ is not needed to perform the search and compute $g$-values; it is only needed to reconstruct the solution path once the search terminates.

Therefore, it suffices to use pointers referring to the machine's local entry for that state. These pointers need not be communicated until the search terminates. At that point, the path can be obtained by walking backwards from the goal. At each step, we move from the current state $s$ to the neighbor $s'$ which minimizes $g(s') + c(s',s)$ among the possible parents $s'=bp(s)$ pooled from all machines. Although we still end up sending full state representations, these are only for the parents of states along the path.
